Create CHaMP map

### 2020-02-05 analysis/R_scripts/compile_wtsd_bndry.Rmd
added chunk to make a map that can be saved and imported into the manuscript.

>>>>

Now let's make a map that we can import into the manuscript

```{r}
champ_wtsds = read_rds('../data/derived_data/champ_wtds.rds')
river_lines = QRFcapacity::get_flowlines(stream_order = 6,
                                         champ_wtsds %>%
                                           st_union() %>%
                                           st_make_grid(n = 1)) %>%
            filter(!grepl('^1701', reachcode),
                   !grepl('^171', reachcode))

# river_lines %>%
#   filter(!gnis_name %in% c('Deschutes River',
#                            'Crooked River',
#                            'Payette River',
#                            'North Fork Payette River')) %>%
#   ggplot() +
#   geom_sf(aes(color = gnis_name))

wtsd_map = ggplot(data = champ_wtsds) +
  geom_sf(data = river_lines %>%
            filter(!gnis_name %in% c('Deschutes River',
                                     'Crooked River',
                                     'Payette River',
                                     'North Fork Payette River')),
          color = 'darkblue') +
  geom_sf() +
  geom_sf(data = champ_wtsds %>%
            filter(fish_data),
          fill = 'black') +
  geom_sf_label(aes(label = id),
                position = position_dodge(width = 200)) +
  theme(axis.title = element_blank())

# save a couple versions
ggsave('../figures/ChampWtds.svg',
       wtsd_map,
       height = 6,
       width = 6)
ggsave('../figures/ChampWtds.png',
       wtsd_map,
       height = 6,
       width = 6)
```
